### 2022-06-03 head/acknowledgements.tex
Add files via upload

I wish to express my deepest gratitude to my supervisor, Damir Filipović, for his guidance and continuous support during these five years. This thesis greatly benefited from his many valuable comments and flow of smart ideas. He guided me and I learned a lot from him about doing research. For this, I am truly grateful.

@@

During these years I had the chance to work with extremely nice and intelligent people. I am thankful to my colleagues and friends Antoine Didisheim and Coralie Jaunin for the countless chess games and `bridge tours` around the campus.

I would like to thank my family: my parents Jacques and Sonia, my sister Isabelle and her husband Edward and my fiancée Cathy for their unconditional love and for bearing all my endless monologues about my latest algorithms. I dedicate this thesis to them.

>>>>

I wish to express my deepest gratitude to my supervisor, Damir Filipović, for his availability and continuous support during these five years. This thesis greatly benefited from his countless valuable comments and flow of smart ideas. He guided me and I learned a lot from him about doing research. For this, I am truly grateful.

@@

During these years I had the chance to work with extremely nice and intelligent people. I am thankful to my colleagues and friends Antoine Didisheim and Coralie Jaunin for the many chess games and `bridge tours` around the campus.

I would like to thank my family: my parents Jacques and Sonia, my sister Isabelle and her husband Edward, my nephew Dylan and my fiancée Cathy for their unconditional love and for bearing all my endless monologues about my latest models. I dedicate this thesis to them.

### 2022-06-03 main/paper1.tex
Add files via upload

\end{tikzpicture}
\caption{Example of the lifespan of a firm. Each dot corresponds to a time period where the econometrician gathers firm-specific (if available) and macroeconomic variables. $t^0_i$ is the entry time of the firm i and $\tau_{D_i}$ denotes the default time of the firm i.}
\label{fig:lifespan}
\end{figure}

@@

    % Annotate the layers
    \node[annot,left of=hl1] {Input Layer};
    \node[annot,right of=hl\Nhidden] {Output Layer};
\end{tikzpicture}
    \caption{Illustration of a neural network [5, 3]. In this network, there are three input features, five neurons in the first hidden layer and 3 neurons in the second hidden layer. Each neuron is activated with a sigmoid function.}
    \label{fig:net}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{def_surv_oe_plot.jpg}
    \caption{Number of firms defaulted, exited for other reasons, surviving each year}
    \label{fig:defsurv}
\end{figure}

\begin{table}[]
    \centering
    \begin{tabular}{l l l l}
    \hline\hline
Horizon & Surviving & Defaults & Other exits \\
    \hline
0 &  2'025'094 & 499 & 10'392\\
%1 &  2'007'311 & 497 & 10'384\\
%2 &  1'989'548 & 483 & 10'173\\
3 &  1'972'063 & 514 & 10'746\\
%4 &  1'953'935 & 511 & 10'743\\
%5 &  1'935'839 & 481 & 10'503\\
6 &  1'918'061 & 499 & 10'713\\
%7 &  1'900'041 & 495 & 10'712\\
%8 &  1'882'058 & 460 & 10'433\\
%9 &  1'864'422 & 468 & 10'611\\
%10 &  1'846'587 & 463 & 10'610\\
%11 &  1'828'772 & 445 & 10'324\\
12 &  1'811'323 & 454 & 10'393\\
%13 &  1'793'797 & 453 & 10'387\\
%14 &  1'776'301 & 433 & 10'037\\
%15 &  1'759'250 & 434 & 10'073\\
%16 &  1'742'157 & 432 & 10'070\\
%17 &  1'725'084 & 416 & 9'770\\
%18 &  1'708'387 & 417 & 9'796\\
%19 &  1'691'651 & 416 & 9'793\\
%20 &  1'674'942 & 391 & 9'434\\
%21 &  1'658'690 & 392 & 9'451\\
%22 &  1'642'418 & 390 & 9'446\\
%23 &  1'626'160 & 381 & 9'183\\
24 &  1'610'242 & 382 & 9'193\\
%25 &  1'594'311 & 381 & 9'189\\
%26 &  1'578'397 & 369 & 8'863\\
%27 &  1'562'910 & 370 & 8'871\\
%28 &  1'547'409 & 370 & 8'867\\
%29 &  1'531'923 & 358 & 8'605\\
%30 &  1'516'819 & 360 & 8'606\\
%31 &  1'501'703 & 359 & 8'601\\
%32 &  1'486'610 & 342 & 8'283\\
%33 &  1'471'935 & 343 & 8'296\\
%34 &  1'457'240 & 343 & 8'295\\
35 &  1'457'240 & 343 & 8'295 \\
\hline
    \end{tabular}
    \caption{Number of firms in each category for each horizon of prediction $\tau$ which corresponds to the firm-month observations used in the likelihood for horizon $\tau$}
    \label{tab:observ}
\end{table}

@@

\begin{table}[]
    \centering
    \begin{tabular}{lrrr}
    \hline \hline
                 & Surviving &   Default  & Other exits \\
    \hline
Cash/TA          &  0.1952 &  0.1896  &    0.1851 \\
NI/TA            & -0.0756 & -0.2057  &   -0.129 \\
Size             & -2.7845 & -4.6743  &   -3.621 \\
DtD              & 10.641 &  6.441  &    8.401 \\
MBratio          &  2.3774 &  1.6995  &    2.202 \\
$\Delta$ CASH/TA  & -0.0026 &  0.0023  &   -0.0074 \\
$\Delta$   NI/TA     & -0.0019 & -0.0433  &   -0.0148 \\
$\Delta$  Size      & -0.0305 & -0.5095  &   -0.0939 \\
$\Delta$   DtD       & -0.1366 & -0.7346  &    0.0295 \\
$\Delta$  MBratio   & -0.0285 &  0.0520  &    0.0801 \\
\hline
    \end{tabular}
    \caption{Mean of variables for surviving firms, defaulted firms and other exits. $\Delta$ are one period lagged differences.}
    \label{tab:meanvar}
\end{table}

\begin{figure}[]
    \centering
    \includegraphics[scale=0.6]{corrmatrix.jpeg}
    \caption{Correlation matrix for firm-specific and macroeconomic covariates}
    \label{fig:corrmat}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{duan_vs_NN.jpeg}
    \caption{Gini coefficient : Linear vs Neural Networks}
    \label{fig:ginicomp}
\end{figure}

@@

\begin{figure*}
        \centering
        \begin{subfigure}[b]{0.48\textwidth}
            \centering
            \includegraphics[width=\textwidth]{0.png}
            \caption*{Horizon 0}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{3.png}
            \caption*{Horizon 3}  
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{6.png}
            \caption*{Horizon 6}   
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{12.png}
            \caption*{Horizon 12}   
        \end{subfigure}
                \vskip\baselineskip
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{24.png}
            \caption*{Horizon 24}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{35.png}
            \caption*{Horizon 35}  
        \end{subfigure}
        \caption{Out-of-sample Lorenz Curves for each horizon. The orange line shows the performance of Duan's model and the red line shows the performance of the [5,3] neural network.} 
        \label{fig:perf}
    \end{figure*}

\begin{table}[]
    \centering
    \begin{tabular}{lll}
\hline
Horizon	&	[5, 3]	&	Linear	\\
\hline \hline
0	&	0.85	&	0.70	\\
%1	&	0.83	&	0.66	\\
%2	&	0.80	&	0.71	\\
3	&	0.79	&	0.71	\\
%4	&	0.79	&	0.58	\\
%5	&	0.77	&	0.53	\\
6	&	0.76	&	0.64	\\
%7	&	0.78	&	0.61	\\
%8	&	0.77	&	0.68	\\
%9	&	0.70	&	0.58	\\
%10	&	0.76	&	0.57	\\
%11	&	0.76	&	0.70	\\
12	&	0.70	&	0.57	\\
%13	&	0.74	&	0.65	\\
%14	&	0.71	&	0.46	\\
%15	&	0.66	&	0.54	\\
%16	&	0.66	&	0.45	\\
%17	&	0.67	&	0.47	\\
%18	&	0.68	&	0.50	\\
%19	&	0.65	&	0.46	\\
%20	&	0.61	&	0.56	\\
%21	&	0.66	&	0.54	\\
%22	&	0.66	&	0.44	\\
%23	&	0.66	&	0.54	\\
24	&	0.66	&	0.44	\\
%25	&	0.58	&	0.47	\\
%26	&	0.63	&	0.52	\\
%27	&	0.63	&	0.50	\\
%28	&	0.63	&	0.48	\\
%29	&	0.68	&	0.48	\\
%30	&	0.62	&	0.49	\\
%31	&	0.56	&	0.51	\\
%32	&	0.62	&	0.46	\\
%33	&	0.62	&	0.38	\\
%34	&	0.62	&	0.32	\\
35	&	0.57	&	0.39	\\
\hline
    \end{tabular}
    \caption{Gini coefficients}
    \label{tab:ginicoeff}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{lor0duan.png}
    \caption{Comparison with the benchmark model \citet{Duan2012}. The green line shows the performance of the [1] neural network (i.e a single hidden layer with a single neuron) with an exponential activation function. The orange line shows the performance of Duan's model and the red line shows the performance of the [5,3] neural network.}
    \label{fig:lor0duan}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{compgraphr.png}
    \caption{Trained [5, 3] Neural Network for forward default intensity at horizon 0. Negative weights are drawn as blue lines connecting neurons where orange lines show positive weights. The thicker the line, the higher the weight is in absolute value.}
    \label{fig:compgraph}
\end{figure}

@@

\begin{figure*}
\centering
        \begin{subfigure}[b]{\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{legendsensi.JPG}
            {{\small }}    
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.475\textwidth}
            \centering
            \includegraphics[width=\textwidth]{0_corr.png}
            \caption*{Horizon 0}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.475\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{3_corr.png}
            \caption*{Horizon 3}    
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{6_corr.png}
            \caption*{Horizon 6}  
            \captionsetup{position=top}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{12_corr.png}
            \caption*{Horizon 12}  
            \captionsetup{position=top}
        \end{subfigure}
                \vskip\baselineskip
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{24_corr.png}
            \caption*{Horizon 24}  
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{35_corr.png}
            \caption*{\small Horizon 35}
        \end{subfigure}
        \caption{Sensitivities for each horizon.} 
        \label{fig:sensi}
    \end{figure*}

>>>>

\end{tikzpicture}
\mycaption{Example of the lifespan of a firm}{Each dot corresponds to a time period where the econometrician gathers firm-specific (if available) and macroeconomic variables. $t^0_i$ is the entry time of the firm i and $\tau_{D_i}$ denotes the default time of the firm i.}
\label{fig:lifespan}
\end{figure}

@@

    % Annotate the layers
    \node[annot,left of=hl1] {Input Layer};
    \node[annot,right of=hl\Nhidden] {Output Layer};
\end{tikzpicture}
    \mycaption{Illustration of a neural network \text{[}5, 3\text{]}}{In this network, there are three input features, five neurons in the first hidden layer and 3 neurons in the second hidden layer. Each neuron is activated with a sigmoid function.}
    \label{fig:net}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{def_surv_oe_plot.jpg}
    \mycaption{Number of firms defaulted, exited for other reasons, surviving each year}{}
    \label{fig:defsurv}
\end{figure}

\begin{table}[]
    \centering
    \begin{tabular}{l l l l}
    \hline\hline
Horizon & Surviving & Defaults & Other exits \\
    \hline
0 &  2'025'094 & 499 & 10'392\\
%1 &  2'007'311 & 497 & 10'384\\
%2 &  1'989'548 & 483 & 10'173\\
3 &  1'972'063 & 514 & 10'746\\
%4 &  1'953'935 & 511 & 10'743\\
%5 &  1'935'839 & 481 & 10'503\\
6 &  1'918'061 & 499 & 10'713\\
%7 &  1'900'041 & 495 & 10'712\\
%8 &  1'882'058 & 460 & 10'433\\
%9 &  1'864'422 & 468 & 10'611\\
%10 &  1'846'587 & 463 & 10'610\\
%11 &  1'828'772 & 445 & 10'324\\
12 &  1'811'323 & 454 & 10'393\\
%13 &  1'793'797 & 453 & 10'387\\
%14 &  1'776'301 & 433 & 10'037\\
%15 &  1'759'250 & 434 & 10'073\\
%16 &  1'742'157 & 432 & 10'070\\
%17 &  1'725'084 & 416 & 9'770\\
%18 &  1'708'387 & 417 & 9'796\\
%19 &  1'691'651 & 416 & 9'793\\
%20 &  1'674'942 & 391 & 9'434\\
%21 &  1'658'690 & 392 & 9'451\\
%22 &  1'642'418 & 390 & 9'446\\
%23 &  1'626'160 & 381 & 9'183\\
24 &  1'610'242 & 382 & 9'193\\
%25 &  1'594'311 & 381 & 9'189\\
%26 &  1'578'397 & 369 & 8'863\\
%27 &  1'562'910 & 370 & 8'871\\
%28 &  1'547'409 & 370 & 8'867\\
%29 &  1'531'923 & 358 & 8'605\\
%30 &  1'516'819 & 360 & 8'606\\
%31 &  1'501'703 & 359 & 8'601\\
%32 &  1'486'610 & 342 & 8'283\\
%33 &  1'471'935 & 343 & 8'296\\
%34 &  1'457'240 & 343 & 8'295\\
35 &  1'457'240 & 343 & 8'295 \\
\hline
    \end{tabular}
    \mycaption{Number of firms in each category for each horizon of prediction $\tau$}{These correspond to the firm-month observations used in the likelihood for horizon $\tau$.}
    \label{tab:observ}
\end{table}

@@

\begin{table}[]
    \centering
    \begin{tabular}{lrrr}
    \hline \hline
                 & Surviving &   Default  & Other exits \\
    \hline
Cash/TA          &  0.1952 &  0.1896  &    0.1851 \\
NI/TA            & -0.0756 & -0.2057  &   -0.129 \\
Size             & -2.7845 & -4.6743  &   -3.621 \\
DtD              & 10.641 &  6.441  &    8.401 \\
MBratio          &  2.3774 &  1.6995  &    2.202 \\
$\Delta$ CASH/TA  & -0.0026 &  0.0023  &   -0.0074 \\
$\Delta$   NI/TA     & -0.0019 & -0.0433  &   -0.0148 \\
$\Delta$  Size      & -0.0305 & -0.5095  &   -0.0939 \\
$\Delta$   DtD       & -0.1366 & -0.7346  &    0.0295 \\
$\Delta$  MBratio   & -0.0285 &  0.0520  &    0.0801 \\
\hline
    \end{tabular}
    \mycaption{Mean of variables for surviving firms, defaulted firms and other exits}{$\Delta$ are one period lagged differences.}
    \label{tab:meanvar}
\end{table}

\begin{figure}[]
    \centering
    \includegraphics[scale=0.6]{corrmatrix.jpeg}
    \mycaption{Correlation matrix for firm-specific and macroeconomic covariates}{}
    \label{fig:corrmat}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{duan_vs_NN.jpeg}
    \mycaption{Gini coefficient : Linear vs Neural Networks}{}
    \label{fig:ginicomp}
\end{figure}

@@

\begin{figure*}
        \centering
        \begin{subfigure}[b]{0.48\textwidth}
            \centering
            \includegraphics[width=\textwidth]{0.png}
            \caption*{Horizon 0}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{3.png}
            \caption*{Horizon 3}  
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{6.png}
            \caption*{Horizon 6}   
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{12.png}
            \caption*{Horizon 12}   
        \end{subfigure}
                \vskip\baselineskip
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{24.png}
            \caption*{Horizon 24}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{35.png}
            \caption*{Horizon 35}  
        \end{subfigure}
        \mycaption{Out-of-sample Lorenz Curves for each horizon}{The orange line shows the performance of Duan's model and the red line shows the performance of the [5,3] neural network.} 
        \label{fig:perf}
    \end{figure*}

\begin{table}[]
    \centering
    \begin{tabular}{lll}
\hline
Horizon	&	[5, 3]	&	Linear	\\
\hline \hline
0	&	0.85	&	0.70	\\
%1	&	0.83	&	0.66	\\
%2	&	0.80	&	0.71	\\
3	&	0.79	&	0.71	\\
%4	&	0.79	&	0.58	\\
%5	&	0.77	&	0.53	\\
6	&	0.76	&	0.64	\\
%7	&	0.78	&	0.61	\\
%8	&	0.77	&	0.68	\\
%9	&	0.70	&	0.58	\\
%10	&	0.76	&	0.57	\\
%11	&	0.76	&	0.70	\\
12	&	0.70	&	0.57	\\
%13	&	0.74	&	0.65	\\
%14	&	0.71	&	0.46	\\
%15	&	0.66	&	0.54	\\
%16	&	0.66	&	0.45	\\
%17	&	0.67	&	0.47	\\
%18	&	0.68	&	0.50	\\
%19	&	0.65	&	0.46	\\
%20	&	0.61	&	0.56	\\
%21	&	0.66	&	0.54	\\
%22	&	0.66	&	0.44	\\
%23	&	0.66	&	0.54	\\
24	&	0.66	&	0.44	\\
%25	&	0.58	&	0.47	\\
%26	&	0.63	&	0.52	\\
%27	&	0.63	&	0.50	\\
%28	&	0.63	&	0.48	\\
%29	&	0.68	&	0.48	\\
%30	&	0.62	&	0.49	\\
%31	&	0.56	&	0.51	\\
%32	&	0.62	&	0.46	\\
%33	&	0.62	&	0.38	\\
%34	&	0.62	&	0.32	\\
35	&	0.57	&	0.39	\\
\hline
    \end{tabular}
    \mycaption{Gini coefficients}{}
    \label{tab:ginicoeff}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{lor0duan.png}
    \mycaption{Comparison with the benchmark model \citet{Duan2012}}{The green line shows the performance of the [1] neural network (i.e a single hidden layer with a single neuron) with an exponential activation function. The orange line shows the performance of Duan's model and the red line shows the performance of the [5,3] neural network.}
    \label{fig:lor0duan}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{compgraphr.png}
    \mycaption{Trained \text{[}5, 3\text{]} Neural Network for forward default intensity at horizon 0}{Negative weights are drawn as blue lines connecting neurons where orange lines show positive weights. The thicker the line, the higher the weight is in absolute value.}
    \label{fig:compgraph}
\end{figure}

@@

\begin{figure*}
\centering
        \begin{subfigure}[b]{\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{legendsensi.JPG}
            {{\small }}    
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.475\textwidth}
            \centering
            \includegraphics[width=\textwidth]{0_corr.png}
            \caption*{Horizon 0}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.475\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{3_corr.png}
            \caption*{Horizon 3}    
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{6_corr.png}
            \caption*{Horizon 6}  
            \captionsetup{position=top}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{12_corr.png}
            \caption*{Horizon 12}  
            \captionsetup{position=top}
        \end{subfigure}
                \vskip\baselineskip
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{24_corr.png}
            \caption*{Horizon 24}  
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.475\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{35_corr.png}
            \caption*{\small Horizon 35}
        \end{subfigure}
        \mycaption{Sensitivities for each horizon}{}
        \label{fig:sensi}
    \end{figure*}
